Papers I Love

### 2017-09-09 texts/dev/PapersILove.tex
update in papers
san diego alg course in cpp
.

\subsubsection{Generic Programming}
	\begin{enumerate}
	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.html}}
	\end{enumerate}
\subsubsection{Dynamic Dispatch}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}

\subsection{Database}
\begin{enumerate}
	\item {The Ubiquitous B-Tree\\
\url{http://people.cs.aau.dk/~simas/aalg06/UbiquitBtree.pdf}}
	\item {Generalized Search Trees for Database Systems\\
\url{http://db.cs.berkeley.edu/papers/vldb95-gist.pdf}}
	\item {Concurrency and Recovery in Generalized Search TreeS\\
\url{http://db.cs.berkeley.edu/papers/sigmod97-gist.pdf}}
	\item {Data Cube: A Relational Aggregation Operator Generalizing Group-By, Cross-Tab, and Sub-Totals\\
\url{http://research.microsoft.com/pubs/69578/tr-95-22.pdf}}
	\item {Query Optimization in Microsoft Sql Server PDW\\
\href{http://academic.research.microsoft.com/Publication/56916436/query-optimization-in-microsoft-sql-server-pdw}{http://academic.research.microsoft.com/Publication/56916436/query-optimization-in-microsoft-sql-server-pdw}}
	\item {Druid: A Real-Time Analytical Data Store
\url{http://static.druid.io/docs/druid.pdf}}
	\item {Map-Reduce: Simplified Dataprocessing on Large Clusters\\
\url{http://static.googleusercontent.com/media/research.google.com/en/us/archive/mapreduce-
	osdi04.pdf}}
	\item {Google’s Mapreduce Programming Model — Revisited\\
\url{http://www.idt.mdh.se/kurser/cd5100/ht06/MapReduce/Ralf-Laemmel-paper/paper.pdf}}
	\item {Cassandra - a Decentralized Structured Storage System\\
\url{http://www.cs.cornell.edu/projects/ladis2009/papers/lakshman-ladis2009.pdf}}
	\item {Bigtable: A Distributed Storage System for Structured Data\\
\url{http://static.googleusercontent.com/media/research.google.com/en//archive/bigtable-osdi06.pdf}}
	\item {Dynamo: Amazon’s Highly Available Key-Value Store\\
\url{http://s3.amazonaws.com/AllThingsDistributed/sosp/amazon-dynamo-sosp2007.pdf}}
	\item {Solving Big Data Challenges for Enterprise Application Performance Management\\
\url{http://vldb.org/pvldb/vol5/p1724_tilmannrabl_vldb2012.pdf}}
\end{enumerate}

@@

\section{Mathematics}
\subsection{Real Analysis}
\begin{enumerate}
	\item {Coisas que o Luís precisa aprender\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
	\item{TEACHING SURVEY SAMPLING WITH THE ‘SAMPLING’ R PACKAGE
	\url{http://iase-web.org/documents/papers/icots8/ICOTS8_4J1_TILLE.pdf}}
	\item{Data Mining and Statistics: What's the Connection\\ \url{http://docs.salford-systems.com/dm-stat.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}

>>>>

\subsubsection{Generic Programming}
	\begin{enumerate}
	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.html}}
	\end{enumerate}
\subsubsection{Dynamic Dispatch}
\subsubsection{Functional Programming}
\begin{enumerate}
	\item {Monadic Parser Combinators\\
\url{http://www.cs.nott.ac.uk/~pszgmh/monparsing.pdf}}
\end{enumerate}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}

\subsection{Database}
\begin{enumerate}
	\item {The Ubiquitous B-Tree\\
\url{http://people.cs.aau.dk/~simas/aalg06/UbiquitBtree.pdf}}
	\item {Generalized Search Trees for Database Systems\\
\url{http://db.cs.berkeley.edu/papers/vldb95-gist.pdf}}
	\item {Concurrency and Recovery in Generalized Search TreeS\\
\url{http://db.cs.berkeley.edu/papers/sigmod97-gist.pdf}}

	\item {Data Cube: A Relational Aggregation Operator Generalizing Group-By, Cross-Tab, and Sub-Totals\\
	\url{http://research.microsoft.com/pubs/69578/tr-95-22.pdf}}
	\item {Query Optimization in Microsoft Sql Server PDW\\
\href{http://academic.research.microsoft.com/Publication/56916436/query-optimization-in-microsoft-sql-server-pdw}{http://academic.research.microsoft.com/Publication/56916436/query-optimization-in-microsoft-sql-server-pdw}}
	\item {Druid: A Real-Time Analytical Data Store
\url{http://static.druid.io/docs/druid.pdf}}
	\item {Map-Reduce: Simplified Dataprocessing on Large Clusters\\
\url{http://static.googleusercontent.com/media/research.google.com/en/us/archive/mapreduce-
	osdi04.pdf}}
	\item {Google’s Mapreduce Programming Model — Revisited\\
\url{http://www.idt.mdh.se/kurser/cd5100/ht06/MapReduce/Ralf-Laemmel-paper/paper.pdf}}
	\item {Cassandra - a Decentralized Structured Storage System\\
\url{http://www.cs.cornell.edu/projects/ladis2009/papers/lakshman-ladis2009.pdf}}
	\item {Bigtable: A Distributed Storage System for Structured Data\\
\url{http://static.googleusercontent.com/media/research.google.com/en//archive/bigtable-osdi06.pdf}}
	\item {Dynamo: Amazon’s Highly Available Key-Value Store\\
\url{http://s3.amazonaws.com/AllThingsDistributed/sosp/amazon-dynamo-sosp2007.pdf}}
	\item {Solving Big Data Challenges for Enterprise Application Performance Management\\
\url{http://vldb.org/pvldb/vol5/p1724_tilmannrabl_vldb2012.pdf}}
\end{enumerate}

@@

\section{Mathematics}
\subsection{Linear Algebra}
\begin{enumerate}
	\item {Basic Linear Algebra Subprograms for Fortran Usage\\
\url{https://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/19780018835.pdf}}
	\item{FLAME: Formal Linear Algebra Methods Environment\\
\url{http://tinyurl.com/ycxkmzw7}}
	\item{The Five Greatest Applications of Markov Chains\\
\url{http://langvillea.people.cofc.edu/MCapps7.pdf}}
\end{enumerate}
\subsection{Real Analysis}
\begin{enumerate}
	\item {Coisas que o Luís precisa aprender\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
	\item{TEACHING SURVEY SAMPLING WITH THE ‘SAMPLING’ R PACKAGE
	\url{http://iase-web.org/documents/papers/icots8/ICOTS8_4J1_TILLE.pdf}}
	\item{Data Mining and Statistics: What's the Connection\\ \url{http://docs.salford-systems.com/dm-stat.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}
